---
title: "in-class-02-Sun"
output: html_document
---

read.table(rnf6080.dat)

# In-Class: September 19, 2018


## Part 1 (You can do this with or without dplyr)

1. The data set at rnf6080.dat records hourly rainfall at a certain location in Canada, every day from 1960 to 1980. First, we need to load the data set into R using the command read.table(). Use the help function to learn what arguments this function takes. Once you have the necessary input, load the data set into R and make it a data frame called rain.df.

```{r}
library(dplyr)
rnf6080 <- read.table("~/Downloads/rnf6080.dat", quote="\"", comment.char="")

rain.df=data.frame(rnf6080)
dim(rain.df)
```



2. How many rows and columns does rain.df have? (If there are not 5070 rows and 27 columns, something is wrong; check the previous part to see what might have gone wrong in the previous part.)
```{r}
dim(rain.df)
```

3. What are the names of the columns of rain.df?
```{r}
colnames(rain.df)
```


4. What is the value of row 5, column 7 of rain.df?
```{r}
rain.df[5,7]
```


5. Display the second row of rain.df in its entirety.
```{r}
rain.df[2,]
```


6. Explain what the command below doesby running it on your data and examining the object. (You may find the display functions head() and tail() useful here.) Is it clear now what the last 24 columns represent?


```
names(rain.df) <- c("year","month","day",seq(0,23))

```{r}
names(rain.df) <- c("year","month","day",seq(0,23))

```
This command assign new names to the each colomn of this dataframe. The last 24 columns represents the 24 hours of a day.

````
7. Create a new column in the data frame called daily, which is the sum of the rightmost 24 columns. With this column, create a histogram of the values in this column, which are supposed to be daily rainfall values. What is wrong with this picture?
```{r}
rain.df=mutate(rain.df,daily=apply(rain.df[,4:27],1,sum))
hist(rain.df$daily)
```
There are some negative values of rainfall, which can not be negative.



8. Create a new data frame rain.df.fixed that takes the original and fixes it for the apparent flaw you have discovered. Having done this, produce a new histogram with the corrected data and explain why this is more reasonable.
```{r}
rain.df.fix=rain.df[,-28]
rain.df.fix[rain.df.fix<0]=NA
rain.df.fix=mutate(rain.df.fix,daily=apply(rain.df.fix[,4:27],1,sum))
hist(rain.df.fix$daily)
```

Our group change the negative observations to NA, thus there will not be any negative rainfalls at any time point. Then we calculate the total rainfall of a day, and still called it "daily". We can see there are no negative values in the daily from the histogram.

